Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-08 paper/paper.tex
Add related work section on partitioning

>>>>

The traditional approach to optimizing network usage in distributed query processing is to apply smart key placement strategies to minimize the number of distributed transactions, and also the amount of data which must be transferred between nodes.
For example, Schism~\cite{Curino2010} uses graph partitioning techniques to reduce the cost of distributed transactions by up to 30\%.
Vila\c{c}a et al.~\cite{Vilaca2011} specifically target key-value stores and aim to improve locality in a multidimensional space of tags (such as foreign keys) applied to data items.
We expect partitioning techniques such as these to be complementary to our work.
